Visually pleasing knot projections

### 2022-06-07 inst/jma_rebuttal_review3.tex

Page 4 line 48: ``However, if we can ensure that the radius of
curvature changes only by a small amount,..."  -$>>$ HOW can the user do
this?

Page 4 lines 50-52: No need to differentiate here between over- and
under-strands.  I assume they are treated the same in the optimization
process.

Page 4 lines 53-54: ``We would like strand crossing points to be far
from nodes,..."  -- Why?  The curves are also visually continuous across
the nodes!

\textcolor{blue}{The curves certainly are visually continuous across
  the nodes---but only in the optimized knots.  Figure 4, for example,
  illustrates an unoptimized knot and we see that the Bezier nodes can
  exhibit ugly features.  The motivation for keeping Bezier nodes far from crossing points 
I have added a
  figure of a trefoil knot that illustrates the reason why nodes'
  being at crossing points is undesirable.  In short, at the node of a
  Bezier curve, the radius of curvature undergoes a visually jarring
  discontinuity which looks bad, especially the understrand, which is
  particularly susecptible to such considerations because of the
  break.\\ \\ Also (refer to figure 5, which shows 7_6 with numbered
  strands), we can see that if a Bezier

}

### 2022-06-07 inst/jma_knot.tex
more work
further work on #58

\begin{figure}[h]
  \centering
    \includegraphics[width=10cm]{trefoil_circles_post_inkscape.pdf}
\caption{A trefoil knot \label{trefoil_circles} constructed from arcs
  of circles (elastica) constrained to cross at right angles; the
  strands exert a couple but no force on one another.  Mirror symmetry
  and threefold rotational symmetry follow.  Elementary trigonometry
  shows that the radii of the inner and outer loops are
  $\operatorname{cosec}(\pi/12)=\sqrt{6}+\sqrt{2}$ and
  $\sec(\pi/12)=\sqrt{6}-\sqrt{2}$ respectively.  The curvature thus
  has a displeasing discontinuity at a node which interrupts the
  visual continuity there, especially the understrand}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
    \includegraphics[width=10cm]{trefoil_circles_post_inkscape.pdf}
\caption{A trefoil knot \label{trefoil_circles} constructed from arcs
  of circles (elastica) constrained to cross at right angles; the
  strands exert a couple but no force on one another.  Mirror symmetry
  and threefold rotational symmetry are imposed.  Elementary
  trigonometry shows that the radii of the inner and outer loops are
  $\operatorname{cosec}(\pi/12)=\sqrt{6}+\sqrt{2}$ and
  $\sec(\pi/12)=\sqrt{6}-\sqrt{2}$ respectively.  The curvature thus
  has a displeasing discontinuity at a node which interrupts the
  visual continuity there, especially the understrand}
\end{figure}

\begin{figure}[h]
  \centering  
  % To create file "two_trefoil_knots_post_inkscape.pdf", run
  % knotter.R, which makes (among other things) two_trefoil_knots.pdf.
  % Edit this in inkscape [make a mirror image, then change the
  % colours and finally use the raise and lower tools to put
  % everything in the right order]
    \includegraphics[width=10cm]{two_trefoil_knots_post_inkscape.pdf}
    \caption{Two trefoil knots \label{two_trefoil_knots}.  Left,
      optimized as per the {\tt knotR} package techniques documented
      here; right, constructed from arcs of circles constrained to
      cross at right angles.  The strands exert a couple but no force
      on one another.  Mirror symmetry and threefold rotational
      symmetry are imposed.  Elementary trigonometry shows that the
      radii of the inner and outer loops are
      $\operatorname{cosec}(\pi/12)=\sqrt{6}+\sqrt{2}$ and
      $\sec(\pi/12)=\sqrt{6}-\sqrt{2}$ respectively.  The curvature
      thus has a displeasing discontinuity at a node which interrupts
      the visual continuity there, especially the understrand}
\end{figure}
